---
title: "Assignment Cereals"
author: "Shude Guo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data Preprocessing
```{r}
library(cluster)
library(factoextra)
library(tidyverse)
setwd("~/Desktop")
Cereals <- read.csv("Cereals.csv")
C <- na.omit(Cereals)
head(C)
str(C)
df <- scale(C[,-c(1:3)])
head(df)
C$mfr <- as.factor(C$mfr)
C$type <- as.factor(C$type)
C <- cbind(C[,1:3],df)
head(C)
```

### Hierarchical clustering
```{r}
d1 <- dist(df, method = "euclidean")
hc_single <- agnes(d1, method = "single")
hc_complete <- agnes(d1, method = "complete")
hc_average <- agnes(d1, method = "average")
hc_ward <- agnes(d1, method = "ward")
print(hc_single)
print(hc_complete)
print(hc_average)
print(hc_ward)
```

#### Best method: hc_ward - Agglomerative coefficient:  0.9046042

#### Cluster: 6, k=6

```{r}
pltree(hc_ward, cex = 0.6, hang = -1, main = "Dendrogram of agnes")
rect.hclust(hc_complete, k = 6, border = "red")
```

```{r}
Partition_A <- df[1:40,]
A <- scale(Partition_A)
Partition_B <- df[41:74,]
B <- scale(Partition_B)
dA <- dist(A, method = "euclidean")
hc_A <- hclust(dA, method = "ward.D")
cA <- cutree(hc_A, k = 6)
table(cA)
c1 <- tapply(A, list(rep(cutree(hc_A, 6), ncol(A)), col(A)), mean)
c1
```

#### To find a cluster of "healthy cereals," the data should not be standardized. Because if the units and properties of the data are not consistent, data standardization is needed to eliminate the impact of dimension on different data. But in order to find "healthy cereals", we can find a unified standard of data to facilitate the target, such as a unified unit of calorie content. However, data standardization is required if comprehensive evaluation of multiple data is required. Since there are different units in different evaluation standards, data standardization is required to eliminate the impact of dimension, variation and value of variables.