---
title: "Mid-Term Examination"
author: "Shude Guo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(factoextra)
library(ISLR)
library(flexclust)
setwd("~/Desktop")
Universities <- read.csv("Universities.csv")
```

### Question 1
```{r}
U <- na.omit(Universities)
head(U)
```

### Question 2
```{r}
set.seed(123)
df <- U[,c(4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)]
df <- scale(df)
distance <- get_dist(df)
fviz_dist(distance)
fviz_nbclust(df, kmeans, method = "wss")
k5 <- kmeans(df, centers = 5, nstart = 25)
k5$centers
k5$size
fviz_cluster(k5, data = df)
```

#### 5 clusters reasonable for describing these data.
#### Optimal K = 5

### Question 3
#### Cluster 1: High application rate, high admission rate, high enrollment rate, high full-time undergraduate rate, low tuition.
#### Cluster 2: Low composite index, lower faculty with PHD ratio.
#### Cluster 3: Composite index is relatively average, low tuition, higher student and faculty ratio.
#### Cluster 4: Composite index is relatively average.
#### Cluster 5: Higher ratio on students from the top 10% and top 25%, higher tuition, higher ratio of room and board, higher faculty with PHD ratio, lower student and faculty ratio, higher graduation rate.

### Question 4
```{r}
U_clustered <- data.frame(U, cluster=factor(k5$cluster))
ggplot(U_clustered, aes(x=U$State, y=U$Public..1...Private..2., color=cluster)) + geom_point()
```

#### Clusters 1 and 3 are mostly distributed in public schools sector, while clusters 2, 4 and 5 are mostly distributed in private schools sector.

### Question 5
#### Clusters 1 and 3 are characterized by high tuition , while clusters 1 and 3 are mostly distributed in public schools. In addition, cluster 1 has the characteristics of high application rate, admission rate and enrollment rate, and cluster 3 has the higher ratio of students and faculty, which indicates that public schools have the characteristics of high tuition fee and higher admission rate.
#### The data of cluster 5 has the characteristics of lower student and faculty ratio, while cluster 2 and 4 also have a medium and low ratio in the student and faculty ratio. It can be inferred that private schools have higher admission thresholds, or lower application and acceptance rates.

### Question 6
```{r}
k5
```
```{r}
set.seed(123)
k5 = kcca(df, k=5, kccaFamily("kmeans"))
k5
clusters_index <- predict(k5)
dist(k5@centers)
image(k5)
points(df, col=clusters_index, pch=19, cex=0.3)
```

